IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/formal.tex

However, even non-adversarial schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI:
%
consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |canFlowTo2 pub sec|, but |cantFlowTo2 sec pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS1 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, but |ic1| will reduce 
(in two steps) 
to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Setion~\ref{sec:extensions}.}
then the |sec| tasks's decision to diverge or not is directly leaked to a
public entity.

>>>>

However, even non-adversarial schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI:
%
consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |canFlowTo2 pub sec|, but |cantFlowTo2 sec pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS1 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, but |ic1| will reduce 
(in two steps) 
to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Section~\ref{sec:extensions}.}
then the |sec| task's decision to diverge or not is directly leaked to a
public entity.

### 2014-03-02 paper/related.tex
rm dead text
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
capitalize titles.

\section{Related work}
\label{sec:related}

@@

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in less false alarms and target legacy code, it comes at the
cost of complexity (the system must accomodate the entirety of JavaScript's
semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
higher than 100\%!~\cite{JSFlow}.  Alternatively, coarse-grained approaches have
also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}. \Red{Different
from them, we rely on programming level abstraction to isolate
computations.}

>>>>

\section{Related Work}
\label{sec:related}

@@

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in less false alarms and target legacy code, it comes at the
cost of complexity (the system must accommodate the entirety of JavaScript's
semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
higher than 100\%!~\cite{JSFlow}.  Alternatively, coarse-grained approaches have
also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.
